Large scale risks from pesticides in small streams

### 2016-10-20 article.tex
main text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% 150-200 words
Small streams are important refugia for biodiversity.
In agricultural areas they may be at high risk from pesticide pollution. 
However, most related studies have been limited to a few streams on the regional level, hampering extrapolation to larger scales. 
We used data from German governmental water quality monitoring to quantify the drivers of pesticide risk and to assess pesticide risk in small streams on a large scale. 
The data set comprised of 1,766,104 measurements related to 24,743 samples in 2,301 sampling sites of 478 pesticides.  
We investigated the influence of agricultural land use, catchment size, as well as precipitation and seasonal dynamics of pesticide risk using new statistical modeling techniques that explicitly consider the limit of quantification. 
Agricultural land use lead to a 3.4-fold increase in exceedance of risk thresholds when the proportion of agriculture in a catchment exceeded 25 percent. 
Precipitation increased measured pesticide risk by 5\% and was the highest during summer months.
Risk thresholds were exceeded in 26 \% of streams, with the highest risk related to neonicotinoid insecticides. 
We conclude that pesticides from agricultural land use are a major threat to small streams and their biodiversity and that a realistic pesticide sampling would be driven precipitation events.

@@

However, small streams might be also at high risk of pesticide contamination from adjacent agricultural areas and lower dilution potential \citep{schulz_field_2004,liess_determination_1999}.
Indeed, meta-analyses using data from studies with a few sites reported higher pesticide pollution in smaller streams compared to bigger streams \citep{stehle_pesticide_2015,schulz_field_2004}.
Despite their ecological relevance and potentially higher pesticide exposure, a recent analysis of pesticide studies showed that a disproportionally small fraction of studies was conducted in small water bodies, and these were largely limited to a few sites \citep{lorenz_specifics_2016}. 
Consequently, knowledge on the pesticide pollution of small streams on larger scales is scant.

@@

where $No(RQ > 1)_i$ is the observed number of RAC exceedances at site $i$. 
We modeled $No(RQ > 1)_i$ as resulting from a negative binomial distribution ($NB$) with mean $\mu_i$ and a quadratic mean-variance-relationship ($Var(No(RQ > 1)_i) = \mu_i + \frac{\mu_i^2}{\kappa}$).
The proportion of agriculture within the catchment ($agri_i$) and the catchment size of the site ($size_i$) were used as predictors of the number of RAC exceedances. 
$\beta_0$ is the intercept and $f_1$ and $f_2$ are smoothing functions using penalized cubic regression splines \citep{wood_generalized_2006}. 
The degree of smoothness was estimated using restricted maximum likelihood (REML) during model fitting process \citep{wood_fast_2011}.
The number of measurements per site ($n_i$) was used as an offset to account for differences in sampling efforts (sampling interval and analysed compound spectrum) at a site and is equivalent to modeling the rate of exceedances. 
We used point-wise 95\% Confidence Intervals (CI) of the first derivative of the fitted smooth to check if there are regions of statistically significant changes.
GAMs were fitted using the mgcv package \citep{wood_fast_2011}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% 150-200 words
Small streams are important refugia for biodiversity.
In agricultural areas they may be at high risk from pesticide pollution. 
However, most related studies have been limited to a few streams on the regional level, hampering extrapolation to larger scales. 
We used data from German governmental water quality monitoring to quantify the drivers of pesticide risk and to assess pesticide risk in small streams on a large scale. 
The data set comprised of 1,766,104 measurements related to 24,743 samples in 2,301 sampling sites of 478 pesticides. 
We investigated the influence of agricultural land use, catchment size, as well as precipitation and seasonal dynamics on pesticide risk using new statistical modeling techniques that explicitly consider the limit of quantification. 
Agricultural land use lead to a 3.4-fold increase in exceedance of risk thresholds when the proportion of agriculture in a catchment exceeded 25 percent. 
Precipitation increased measured pesticide risk by 5\% and was the highest during summer months. 
Risk thresholds were exceeded in 26 \% of streams, with the highest risk related to neonicotinoid insecticides. 
We conclude that pesticides from agricultural land use are a major threat to small streams and their biodiversity and that a realistic pesticide sampling would be driven by q1Qprecipitation events.

@@

However, small streams might also be at high risk of pesticide contamination in case of adjacent agricultural areas given their dilution potential \citep{schulz_field_2004,liess_determination_1999}.
Indeed, meta-analyses using data from studies with a few sites reported higher pesticide pollution in smaller streams compared to bigger streams \citep{stehle_pesticide_2015,schulz_field_2004}. 
Despite their ecological relevance and potentially higher pesticide exposure, a recent analysis of pesticide studies showed that a disproportionally small fraction of studies was conducted in small water bodies, and these were largely limited to a few sites \citep{lorenz_specifics_2016}. 
Consequently, knowledge on the pesticide pollution of small streams on larger scales is scant.

@@

where $No(RQ > 1)_i$ is the observed number of RAC exceedances at site $i$. 
We modeled $No(RQ > 1)_i$ as resulting from a negative binomial distribution ($NB$) with mean $\mu_i$ and a quadratic mean-variance-relationship ($Var(No(RQ > 1)_i) = \mu_i + \frac{\mu_i^2}{\kappa}$).
The proportion of agriculture within the catchment ($agri_i$) and the catchment size of the site ($size_i$) were used as predictors of the number of RAC exceedances. 
$\beta_0$ is the intercept and $f_1$ and $f_2$ are smoothing functions using penalized cubic regression splines \citep{wood_generalized_2006}. 
The degree of smoothness was estimated using restricted maximum likelihood (REML) during model fitting process \citep{wood_fast_2011}.
The number of measurements per site ($n_i$) was used as an offset to account for differences in sampling efforts (sampling interval and analysed compound spectrum) at a site and is equivalent to modeling the rate of exceedances. 
We used point-wise 95\% Confidence Intervals (CI) of the first derivative of the fitted smooth to identify regions of statistically significant changes.
GAMs were fitted using the mgcv package \citep{wood_fast_2011}.
